First and foremost, I would like to thank my supervisor, Dr. R\'{e}gis Pom\`{e}s, for his insight and guidance. My journey in scientific research begun in his lab in 2003 where I was a summer student.  I am grateful that I became older, wiser, and more confident in his lab under his guidance.

I thank my committee members Drs. JoAnne McLaurin, Mark Nitz and Avi Chakrabartty for their advice and for pushing me forward.

I thank the members of my lab, both past and present, for helping me with my work and for providing extensive moral support. Specifically, I would like to thank the early Ph.D. students of the lab, Drs. Chris Madill, Chris Neale, Sarah Rauscher, Tomas Rodinger and Marty Kurylowicz for setting examples of excellence. I especially thank Dr. Nilu Chakrabarti, Dr. John Holyoake, Dr. Chris Neale, David Caplan, Dr. Loan Huynh, Kethika K., and Aditi R. for their help, advice and support in life and in the lab. All of you have contributed substantially in helping me become more mature.

I give my sincerest thanks to Mr. Larry Zimmerman, my high school math teacher and math team coach, and Dr. Nasir Memon for inspiring me and instilling in me a love of mathematics and computer science at a crucial age. You've also taught me the appropriate amount of discipline needed to study and master subjects in these fields.

I thank my family and friends both far and near for their support and encouragement (a.k.a had the patience to endure my venting over the years).  A special thanks to Suraj C. - you met me at the end of this very important journey, but you've been one of the biggest source of encouragement and support thus far. Thank you Ken, Omar and Yelena for all the good times I've had whenever I'm back in NYC and for your support and encouragement during stressful times. 

Finally, I give my deepest thanks to my mom and my grandparents for their unconditional love, support, encouragement, and understanding.
